---
title: "Homework 5"
author: "Keyanna Davis"
date: "11/1/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(knitr)
library(p8105.datasets)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

#Problem 1

The code chunk below loads the `iris` dataset from the `tidyverse` package and introduces some missing values in each column. The purpose of this problem is to fill in those missing values.

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

* For numeric variables, you should fill in missing values with the mean of non-missing values

```{r}

```

* For character variables, you should fill in missing values with "virginica"

```{r}

```

Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement.

```{r}

```

# Problem 2

This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

* Start with a dataframe containing all file names; `the list.files` function will help
* Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
* Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r}

```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}

```

# Problem 3
When designing an experiment or analysis, a common question is whether it is likely that a true effect will be detected – put differently, whether a false null hypothesis will be rejected. The probability that a false null hypothesis is rejected is referred to as power, and it depends on several factors, including: the sample size; the effect size; and the error variance. In this problem, you will conduct a simulation to explore power in a simple linear regression.

First set the following design elements:

* Fix n=30
* Fix xi1 as draws from a standard Normal distribution
* Fix β0=2
* Fix σ2=50
Set β1=0. Generate 10000 datasets from the model
              yi=β0+β1xi1+ϵi
with ϵi∼N[0,σ2]. For each dataset, save β̂1 and the p-value arising from a test of H:β1=0 using α=0.05. Hint: to obtain the estimate and p-value, use broom::tidy to clean the output of lm.

Repeat the above for β1={1,2,3,4,5,6}, and complete the following:

* Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of β2
 on the x axis. Describe the association between effect size and power.
* Make a plot showing the average estimate of β̂1 on the y axis and the true value of β1 on the x axis. Make a second plot (or overlay on the first) the average estimate of β̂1 only in samples for which the null was rejected on the y axis and the true value of β1 on the x axis. Is the sample average of β̂1 across tests for which the null is rejected approximately equal to the true value of β1
? Why or why not?


```{r}

```


